\gettitle

### 2019-12-01 assignment3/submission3.tex
Add solution for Exercise 3.1b

\begin{figure}[ht!]
	\begin{tikzpicture}[scale=0.2]
	\foreach \x in {1,...,81} {
		\draw (\x,0) -- (\x, 2);
		\draw (\x, -5) -- (\x, -7);
	};
	\draw (0,0) -- (81,0);
	\draw (0,-5) -- (81,-5);
	\node at(0, -1) {\tiny Master};
	\node at(0, -4) {\tiny Slave};
	\foreach \x/\n in {3/1,8/2,13/3,18/4,23/5,28/6,33/7,38/8,43/9,48/10,53/11,58/12,63/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,1) (a\n) {}
			node[below=7mm, above of=a\n] {\tiny \n};
	};
	\foreach \x/\n in {3/6,8/7,13/8,18/9,23/10,28/11,41/12,55/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,-6) (b\n) {}
			node[above=7mm, below of=b\n] {\tiny \n};
	};
	\path[draw,->]
		(b8.north) edge (a4.south)
		(a5.south) edge (b11.north);
\end{tikzpicture}
\caption{Solution for Figure 2}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((4 - 8) - (11 - 5)) = \frac12(-4 - 6) = -5  &\\
d = 1 & \\
\Delta = 3, C_s(t_4 + \Delta) = 14 & \\
\frac{dC_S}{dt} = \frac{3}{3 +5} = \frac{3}{8} &
\end{align*}

>>>>

\begin{figure}[ht!]
	\begin{tikzpicture}[scale=0.2]
	\foreach \x in {1,...,81} {
		\draw (\x,0) -- (\x, 2);
		\draw (\x, -5) -- (\x, -7);
	};
	\draw (0,0) -- (81,0);
	\draw (0,-5) -- (81,-5);
	\node at(0, -1) {\tiny Master};
	\node at(0, -4) {\tiny Slave};
	\foreach \x/\n in {3/1,8/2,13/3,18/4,23/5,28/6,33/7,38/8,43/9,48/10,53/11,58/12,63/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,1) (a\n) {}
			node[below=7mm, above of=a\n] {\tiny \n};
	};
	\foreach \x/\n in {3/6,8/7,13/8,18/9,23/10,28/11,41/12,55/13,68/14,73/15,78/16} {
		\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,-6) (b\n) {}
			node[above=7mm, below of=b\n] {\tiny \n};
	};
	\path[draw,->]
		(b8.north) edge (a4.south)
		(a5.south) edge (b11.north);
\end{tikzpicture}
\caption{Solution for Figure 2}
\end{figure}
\begin{align*}
O = \frac12((t_2 - t_1) - (t_4 - t_3)) = \frac12((4 - 8) - (11 - 5)) = \frac12(-4 - 6) = -5  &\\
d = 1 & \\
\Delta = 8, C_s(t_4 + \Delta) = 14 & \\
\frac{dC_S}{dt} = \frac{8 - 5}{8} = \frac{3}{8} &
\end{align*}

\subsection*{b)}
\begin{enumerate}[label=(\roman*)]

	\item We can use the difference in offsets to determine the clockrate of the master node in relation to the subservient node.
	For that purpose we calculate \(O_1 = \frac12((t_6 - t_5) - (t_8 - t_7))\) and \(O_0 = \frac12((t_2 - t_1) - (t_4 - t_3))\).

	It's clear that \(\frac{O_1 - O_0}{t_6 - t_2}\) is the rate at which the clocks are desynchronizing in reference to the master clock.
	If \(O_1 - O_0\) is negative, the subservient clock is faster than the master, and vice versa.
	This means that for negative \(O_1 - O_0\), the frequency ratio is \(f = \frac{t_6 - t_2}{O_0 - O_1}\).
	For a faster master clock the frequency ratio is the desynchronization rate from before.

	\item It makes no sense to synchronize the clock rates before the clock values, because to enable a ''stable'' value synchronization  -- i.e. monotonically increasing without large gaps in tick-time or clockvalues -- the clock frequency needs to be adjusted again.
	As such, the synchronized clock frequency would need to be changed again to synchronize clock values, making it an unnecessary step.

	\item Synchronization of the depicted clocks.
	\begin{align*}
		O_0 = \frac12((5-6)-(9-6)) = 1 & \\
		O_1 = \frac12((8-11) - (14-9)) = -4 & \\
		d = \frac12((8-11) + (14-9)) = 1 & \\
		f = \frac{(8 - 5)}{1 - (-4)} = \frac35 &
	\end{align*}

	We choose \(\Delta = 8, C_s(t_8 + \Delta) = 18\) modifying the clock frequency of \(C_s\) to \(f * \frac{\Delta + O_1}{\Delta}\) of the original frequency.
	When \(t_8 + \Delta\), we again modify the frequency by \(\frac{\Delta}{\Delta - O_1}\) to return to the synchronized clock freqency.

	This means \(\frac{dC_s}{dt} = f * \frac{8 - 4}{8} = f * \frac12 = \frac{3}{10}\)

	\item Completing the figure.
	\begin{figure}[ht!]
		\begin{tikzpicture}[scale=0.2]
		\foreach \x in {1,...,81} {
			\draw (\x,0) -- (\x, 2);
			\draw (\x, -5) -- (\x, -7);
		};
		\draw (0,0) -- (81,0);
		\draw (0,-5) -- (81,-5);
		\node at(0, -1) {\tiny Master};
		\node at(0, -4) {\tiny Slave};
		\foreach \x/\n in {3/4,8/5,13/6,18/7,23/8,28/9,33/10,38/11,43/12,48/13,53/14,58/15,63/16,68/17,73/18,78/19} {
			\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,1) (a\n) {}
				node[below=7mm, above of=a\n] {\tiny \n};
		};
		\foreach \x/\n in {3/5,6/6,9/7,12/8,15/9,18/10,21/11,24/12,27/13,30/14,40/15,50/16,60/17,70/18,75/19,80/20} {
			\draw node[rectangle, fill=black, text width=1mm, inner sep=0, minimum height=4mm] at(\x,-6) (b\n) {}
				node[above=7mm, below of=b\n] {\tiny \n};
		};
		\path[draw,->]
			(b6.north) edge (a5.south)
			(a6.south) edge (b9.north)
			(b11.north) edge (a8.south)
			(a9.south) edge (b14.north);
	\end{tikzpicture}
	\caption{Solution for Figure 2}
	\end{figure}

	Note that the delay is not used in the timing schema proposed in (i).
	It has been included in the calculations for (iii) for completeness' sake.
\end{enumerate}
